---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covid19us

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/aedobbyn/covid19us.svg?branch=master)](https://travis-ci.org/aedobbyn/covid19us)
<!-- badges: end -->

This is an R wrapper around the [COVID Tracking Project API](https://covidtracking.com/api/). It provides updates on the spread of the virus in the US with a few simple functions.

## Installation

``` r
devtools::install_github("aedobbyn/covid19us")
```

## Examples

```{r example}
library(covid)
```

Get the most recent COVID-19 top-line data for the country:

```{r}
get_us_current()
```

Or the same by state:

```{r}
get_states_current()
```

Daily state counts can be filtered by state and/or date:

```{r}
get_states_daily(
  state = "NY", 
  date = "2020-03-17"
)
```

## All Functions

```
get_counties_info
get_states_current
get_states_daily
get_states_info
get_tracker_urls
get_us_current
get_us_daily
```

## Other Details

* All of the data sources can be found with `get_tracker_urls()`
  * The `filter` column gives information about how the [COVID Tracking Project's scraper](https://github.com/COVID19Tracking/covid-tracking) currently scrapes data from the page (xpaths, CSS selectors, functions used, etc.)

* State breakdowns include DC as well as some US territories including American Samoa (AS), Guam (GU), Northern Mariana Islands (MP), Puerto Rico (PR), and the Virgin Islands (VI)

* Time zone used is Eastern Standard Time

***

**[PR](https://github.com/aedobbyn/covid/pulls)s and [bug reports / feature requests](https://github.com/aedobbyn/covid/issues) welcome.** Stay safe!
